Independent discovery of a nulling pulsar with unusual sub-pulse drifting properties with the Murchison Widefield Array

### 2022-06-02 paper/main.tex
Removed all boldface type

To estimate the nulling fraction, we first identified which pulses contained sub-pulses within the pulse window (this is a semi-automated procedure described in \S\ref{sec:drifting_analysis}).
Any pulse without a sub-pulse is then counted as a null, even if it is nested within a burst sequence.
Under this definition, we report a nulling fraction of $\sim$~\nullfraction{},
{\bf
calculated using all six MWA observations (refer to Table \ref{tab:observations}).
Note that if the two observations taken on MJD 59002 are excluded, the nulling fraction would be $\sim$~72\%.
}

>>>>

To estimate the nulling fraction, we first identified which pulses contained sub-pulses within the pulse window (this is a semi-automated procedure described in \S\ref{sec:drifting_analysis}).
Any pulse without a sub-pulse is then counted as a null, even if it is nested within a burst sequence.
Under this definition, we report a nulling fraction of $\sim$~\nullfraction{},
calculated using all six MWA observations (refer to Table \ref{tab:observations}).
Note that if the two observations taken on MJD 59002 are excluded, the nulling fraction would be $\sim$~72\%.
